Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
section 4

%-------------------------------
 \subsubsection{Finding Abstract Supports for Continuous Dynamics}
 \label{sec:cont_aasup}
%-------------------------------

Just as the accelerated dynamics in equation \eqref{eq:feedback_sampled_cont} can be abstacted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
we use the same principle on equation \eqref{eq:feedback_cont} to obtain 
\begin{equation}\label{eq:aa_cont_amatrix}
\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
\end{equation}

@@

We next describe how to obtain such a set. 
Our overapproximation of the set is a polyhedron, which is defined by an
intersection of hypeplanes. The smallest polyhedra that can be obtained are
those whose faces touch the set, which they must do at a point tangential to
the hyperplane. Rather than pick a set of directions and find such points, we
will start from the points and find their tangents. Furthermore, to simplify the
procedure, we will only look at two dimensional cuts of the space 
(see~\cite{cattaruzza2015unbounded}). This means that for every point we
choose is a vertex of the polyhedron.
Finding out which side of the hyperplane corresponds to the inside of the
polyhedron is achieved by looking at any other point in the original set and
checking on which side of the hyperplane it lays.

@@

\textcolor{red}{[Next part highly nebulous]} 
\textcolor{blue}{[This is just the math that calculates the tangents of x-y pairs given the progression of x and y. Given the above description,is it necessary to include it?]}

@@

%-------------------------------
\section{CEGIS of digital controllers} 
\label{sssec:cegisdig}
%-------------------------------

@@

\textcolor{red}{[Elizabeth: please rewrite this]}

>>>>

%-------------------------------
 \subsubsection{Abstract Supports for Continuous Dynamics}
 \label{sec:cont_aasup}
%-------------------------------

Just as the accelerated dynamics in Eqn. \eqref{eq:feedback_sampled_cont} can be abstracted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$), 
we use the same principle on Eqn. \eqref{eq:feedback_cont} to obtain 
\begin{equation}\label{eq:aa_cont_amatrix}
\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
\end{equation}

@@

We next describe how to obtain an over-approximation of such a set. 
This is defined as a polyhedron, expressed as an intersection of hyperplanes. 
A tight polyhedron that can be obtained with faces (hyperplanes) that touch the set. 
%, which they must do at a point tangential to the hyperplane. 
Rather than pick \note{[concept undefined:] a set of directions} and find such points, 
we will start from the points and find their tangents \note{there can be just a single tangent, or possibly multiple ones?}.  
Furthermore, to simplify the procedure, 
we will only look at \note{[qualitative:] two dimensional cuts of the space}  
(see~\cite{cattaruzza2015unbounded}):  
this means that for every point we choose is a vertex of the polyhedron \note{??}. 
Finding out which side of the hyperplane corresponds to the inside of the
polyhedron is achieved by looking at any other point in the original set and
checking on which side of the hyperplane it lays.

@@

\textcolor{red}{[Next part highly nebulous]} 
\textcolor{blue}{[This is just the math that calculates the tangents of x-y pairs given the progression of x and y. Given the above description,is it necessary to include it?]}
\note{I would cut the next part, if possible. However, the explanation above is not clear. It seems like you're just finding a convex hull. You have not introduced the notion of directions. The paragraph above requires brand new thinking. }

@@

%-------------------------------
\section{Synthesis of digital controllers with CEGIS} 
\label{sssec:cegisdig}
%-------------------------------

@@

\textcolor{red}{[We call this approach either naive or multi-stage. Let us pick a single attribute, which I recommend to be the latter (multi-stage). Naive is excessively debutant.]}
